---
title: "Assignment2"
author: "Weiqun Tong"
date: "April 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is the week 2 assignment project of the Coursera cours-Developing Data Products. I use my own data to draw the map. I am happy to live in different places of the United States. Besides, in the moving process, I passed more than 20 states. This is cool!

## Data plotted
I have lived in 5 citys of 5 states after I arrived in the United States in 2003. The living experience in those cities reminds me great moments of my past years.

```{r pressure, echo=TRUE}
library("leaflet")

cities<-data.frame(name=c("Lincoln NE", "Tucson AZ", "San Antonio TX", "Madison WI", "Baltimore MD"),
                   tract = c("First Arrival ", "Degree achieved", "First job", "Second job", "Current job"),
                   col = c("blue", "red", "green", "yellow", "purple"),
                   lat = c(40.8136, 32.2226, 29.4241,43.0731, 39.2904),
                   lng = c(-96.7026, -110.9747, -98.4936, -89.4012, -76.6122))

CitySites <- c(
  "<a href='https://www.lincoln.ne.gov/'>Lincoln</a>",
  "<a href='https://www.tucsonaz.gov/'>Tucson</a>",
  "<a href='https://www.sanantonio.gov/'>San Antonio</a>",
  "<a href='http://www.cityofmadison.com/'>Madison</a>",
  "<a href='https://baltimore.org/'>Baltimore</a>"
)
cities %>% 
  leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addCircleMarkers(~lng, ~lat, color= cities$col, popup=CitySites, label= ~name) %>%
  addLegend(labels=cities$tract, colors=c("blue", "red", "green", "yellow", "purple"))


```


